A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-06 analysis/paper/paper.Rmd
correct chunk header and delete some duplicated figures

image_width_1_col_inch = 90/25.4 # image Single column	w = 90 mm 
image_width_2_col_inch = 190/25.4 # image Double column w = 190 mm 
image_width_3_col_inch = 190/20
```

@@

```{r burial-location, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("001-data-tidy.R"))}
suppressWarnings(source(here::here("analysis", "paper", "002-burial-location.R")))
```

>>>>

image_width_1_col_inch = 90/25.4 # image Single column	w = 90 mm 
image_width_2_col_inch = 190/25.4 # image Double column w = 190 mm 
image_width_3_col_inch = 190/19
```

@@

```{r burial-location, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("002-burial-location.R"))}
suppressWarnings(source(here::here("analysis", "paper", "002-burial-location.R")))
```
